CRUSE to Safe Cycling in Ireland

### 2023-09-14 paper.qmd
Add author contributions

@@

@@

@@

@@

>>>>

Data was obtained from the Central Statistics Office (CSO) and Transport Infrastructure Ireland (TII) under license and cannot be shared publicly.
The code used to generate the results presented in this paper is available at https://github.com/cruse-bike.

@@

The work was funded by Transport Infrastructure Ireland (TII).

@@

Thanks to Paul MacDonald and Donal Hodgins (Kildare County Council),  for testing early versions of the tool and for their input into the project.
Thanks to Ciaran Maguire, Catherine Swift, and others at AECOM for their input into the project.

@@

The authors declare that they have no competing interests.

@@

RL led the development of the CRUSE tool, with input from JT, EV, HM, EB, PW, GOT, DB, and SM.
SM instigated the project and coordinated its policy impact.
PW, EB and GOT provided project management and transport engineering expertise.
